### 2015-05-26 Dissertation/chapter-graybox.tex
Minor fixes

Every problem discussed in Chapter~\ref{chap-problems} except HIFF fit into this domain. Deceptive
Trap and Deceptive Step Trap both can have known epistasis (which bits are in which traps) and
partial reevaluation (score a single trap), the same as Rastrigin (separable). All NK problems
where $K \ll N $ have a knowable epistasis table and the fitness contribution of each is subfunction
calculable without evaluating the entire string. Similarly, MAX-SAT's clause list specifies epistasis,
with each clause independently evaluable. Ising Spin Glasses are even simpler, with each edge in the
graph evaluable using only two problem variables.

@@

\item \textbf{Set Cover}: Given a universe of elements and a set of subsets of that universe,
find a minimum set of subsets whose union recreates the entire universe. Each element in
the universe is epistatically linked with subsets that contain that element (add to uncovered size)
and with each subset also contributing directly to fitness (add to set size). Used in
computational biology~\cite{painsky:2014:setcover}.

>>>>

Every problem discussed in Chapter~\ref{chap-problems} except HIFF fit into this domain. Deceptive
Trap and Deceptive Step Trap both can have known epistasis (which bits are in which traps) and
partial reevaluation (score a single trap), the same as Rastrigin (separable). All NK problems
where $K \ll N $ have a knowable epistasis table and the fitness contribution of each subfunction is
calculable without evaluating the entire string. Similarly, MAX-SAT's clause list specifies epistasis,
with each clause independently evaluable. Ising Spin Glasses are even simpler, with each edge in the
graph evaluable using only two problem variables.

@@

\item \textbf{Set Cover}: Given a universe of elements and a set of subsets of that universe,
find a minimum set of subsets whose union recreates the entire universe. Each element in
the universe is epistatically linked with subsets that contain that element (add to uncovered size)
and each subset also contributes directly to fitness (add to set size). Used in
computational biology~\cite{painsky:2014:setcover}.

### 2015-05-26 Dissertation/chapter-introduction.tex
Minor fixes

There have been periodic efforts to reduce or remove the need for parameter tuning.
\cite{rechenberg:1973:es} introduced self-adaptive parameters, in which parameter values
were included in each solution's genome and themselves underwent evolution. This allowed search
to optimize some of its own parameters, resulting in a reduced need for expert tuning.
\cite{harik:1999:parameterlessga} were able to design an entirely parameter-less GA by
leveraging schema theory and parallel populations. Unfortunately these methods were provably less efficient
than directly setting the parameters to optimal values~\cite{pelikan:1999:worstparameter-less}.

@@

Most recently \cite{goldman:2014:p3} introduced the Parameter-less Population Pyramid~(P3).
This method uses a pyramid structure of populations to combine model based search with local search
to achieve parameter-less optimization. Initial results suggest that unlike
previous parameter-less methods, P3 is actually more efficient than current state-of-the-art
parameterized search algorithms. In this work we shall: extend these results to cover more
comparison algorithms; compare both efficiency in reaching the global optimum and intermediate
fitnesses; analyze algorithm complexity; and provide more in depth analysis of P3 itself.

>>>>

There have been periodic efforts to reduce or remove the need for parameter tuning.
\cite{rechenberg:1973:es} introduced self-adaptive parameters, in which parameter values
were included in each solution's genome and themselves underwent evolution. This allowed search
to optimize some of its own parameters, resulting in a reduced need for expert tuning.
\cite{harik:1999:parameterlessga} was able to design an entirely parameter-less GA by
leveraging schema theory and parallel populations. Unfortunately these methods were provably less efficient
than directly setting the parameters to optimal values~\cite{pelikan:1999:worstparameter-less}.

@@

Most recently we introduced the Parameter-less Population Pyramid~(P3)~\cite{goldman:2014:p3}.
This method uses a pyramid structure of populations to combine model based search with local search
to achieve parameter-less optimization. Initial results suggest that unlike
previous parameter-less methods, P3 is actually more efficient than current state-of-the-art
parameterized search algorithms. In this work we shall: extend these results to cover more
comparison algorithms; compare both efficiency in reaching the global optimum and intermediate
fitnesses; analyze algorithm complexity; and provide more in depth analysis of P3 itself.
